|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
clean up code and replace reported value with inline r code if possible

# a bit stronger
# plot 7 -> plot 2^3 - 1

# vi_survey %>%
#   filter(!attention_check) %>%
#   filter(!null_lineup) %>%
#   filter(type == "polynomial") %>%
#   filter(x_dist == "uniform") %>%
#   filter(n == 300) %>%
#   filter(shape == 1) %>%
#   group_by(unique_lineup_id) %>%
#   summarise(effect_size = first(effect_size)) %>%
#   arrange(effect_size)

@@

```{r eval = FALSE}
mix_effect_dat <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  mutate(reject = p_value < 0.05) %>%
  select(log_effect_size, reject, subject)

# Singularity issue (random effect too small? not worth to fit a mix-effect model?)
mix_mod <- lme4::glmer(reject ~ scale(log_effect_size) + (1 | subject), data = mix_effect_dat, family = binomial())

pred_dat <- map_df(seq(-1, 6, 0.1),
    function(x) {
      result <- data.frame(log_effect_size = rep(x, length(unique(mix_effect_dat$subject))))
      pred <- predict(mix_mod, 
                      type = "response", 
                      newdata = data.frame(log_effect_size = x, 
                                           subject = unique(mix_effect_dat$subject)))
      result$subject <- names(pred)
      result$pred <- pred
      result
    })

pred_dat %>%
  ggplot() +
  geom_line(aes(log_effect_size, pred, group = subject))
```

```{r eval = FALSE}
MASS::glmmPQL(weighted_detect ~ scale(log_effect_size), random = ~ scale(log_effect_size) | subject,  family = quasibinomial(), data = vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  select(log_effect_size, weighted_detect, subject)) -> mod

mod_dat <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  # mutate(log_effect_size = scale(log_effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  select(log_effect_size, weighted_detect, subject)

mod <- lme4::glmer(weighted_detect ~ scale(log_effect_size)  + (scale(log_effect_size) | subject), 
                   family = quasibinomial(),
                   data = mod_dat)

mod_dat$log_effect_size

map(seq(-1, 6, 0.1), ~predict(mod, newdata = data.frame(subject = 1:283, log_effect_size = .x), type = "response")) %>%
  `names<-`()

vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log10(effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  mutate(pred_wd = predict(mod, type = "response")) %>%
  group_by(unique_lineup_id) %>%
  mutate(pred_ci = pred_wd * n()) %>%
  mutate(n_eval = n()) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(pred_pval = (function(c_i, n_eval, alpha) {
  target_dist <- exact_dist(n_eval, 20, dist = "dirichlet", alpha = alpha)
  floor_c_i <- floor(c_i)
  ceil_c_i <- ceiling(c_i)
  return(unname(sum(target_dist[(ceil_c_i:n_eval) + 1]) + (ceil_c_i - c_i) * target_dist[floor_c_i + 1]))
})(pred_ci, n_eval, alpha)) %>%
  ungroup() %>%
  mutate(pred_reject = pred_pval < 0.05) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, as.numeric(pred_reject)), method = "glm", method.args = list(family = binomial()), se = FALSE)

```

Effect $E$ is derived from the Kullback-Leibler divergence (see [appendix ref here]) formulated as

@@

\begin{gather}  \label{eq:effect-size}
E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

@@

To study various factors contributing to the power of the visual test, the same logistic regression model is fit on different subsets of the collated data grouped by levels of factors. These include the distribution of the regressor and the type of the simulated model.

```{r residual-plot-cubic-heter, fig.cap='Residuals vs. fitted values plot for a classical normal linear regression model. The residuals are produced by fitting a two-regressor multiple linear regression model with data generated from a cubic linear model. From the residual plot, "butterfly shape" can be observed which generally would be interpretd as evidence of heteroskedasticity. Further, from the outline of the shape, nonlinear patterns exist. Both visual discoveries are evidence against $H_0$, though heteroskedasticity actually does not exist in the data generating process. \\label{fig:residual-plot-cubic-heter}', eval = FALSE}

cm <- cubic_model(a = 0, b = 100, c = 1)

cm$gen(1000, fit_model = TRUE) %>%
cm$plot() +
  theme_light()
```

@@

Three experiments are conducted to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. Meanwhile, the experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test. The experiment III is designed for collecting human responses to null lineups such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to collect 7974 evaluations on 1152 uniqued lineups performed by 443 subjects throughout three experiments.

@@

<!-- (handbook of mathathetical function, https://aapt.scitation.org/doi/10.1119/1.15378, cite the package) -->

<!-- (hermite poly is created by ... in 18..,) -->

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", ""),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rcrrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Description of all factors involved in the non-linear and heteroskedasticity studies.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Heteroskedasticity Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Heteroskedasticity (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)")) %>% #"Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

@@

```{r different-shape-of-herimite, fig.height = 2, fig.cap="Polynomial forms generated for the residual plots used in experiment I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$."}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300)

pp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(He[2]:"U")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

pp2 <- VI_MODEL$plot(poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote(He[3]:"S")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

pp3 <- VI_MODEL$plot(poly_model(shape = 3, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote(He[6]:"M")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

pp4 <- VI_MODEL$plot(poly_model(shape = 4, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote(He[18]:"Triple-U")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r different-dist, fig.height = 2, fig.cap="Variations in fitted values ($X_{raw}$), that might affect perception of residual plots. Four different distribution are used."}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

dp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle("A. Uniform") + #quote(U(-1,1))) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

dp2 <- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300, computed = select(ori_dat, e))) +
  ggtitle("B. Normal") + #quote(N(0,0.3^2))) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

dp3 <- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))}, sigma = 0.5)$gen(300, computed = select(ori_dat, e))) +
  ggtitle("C. Skewed") + #quote(lognormal(0,0.6^2)/3)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

dp4 <- VI_MODEL$plot(poly_model(shape = 1, x = rand_uniform_d(k = 5, even = TRUE), sigma = 0.5)$gen(300, computed = select(ori_dat, e))) +
  ggtitle("D. Discrete") + #quote(U~"{1,5}")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r different-n, fig.height = 2.67, fig.cap="Three different values of $n$ are used in experiment I, II and III to control the strength of the signal."}
ori_dat <- poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1.5)$gen(300)

np1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(n~"="~300)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

np2 <- VI_MODEL$plot(poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1.5)$gen(50, computed = select(ori_dat[1:50,], x, e))) +
  ggtitle(quote(n~"="~50)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

np3 <- VI_MODEL$plot(poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1.5)$gen(50, computed = select(ori_dat[1:100,], x, e))) +
  ggtitle(quote(n~"="~100)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(np2, np3, np1, ncol = 3)
```

```{r different-sigma, fig.height = 2, fig.cap="Four different values of $\\sigma$ are used in the experiment I to control the strength of the signal."}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

sp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(sigma~"="~0.5)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

sp2 <- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1)$gen(300, computed = select(ori_dat, x))) +
  ggtitle(quote(sigma~"="~1)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

sp3 <- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 2)$gen(300, computed = select(ori_dat, x))) +
  ggtitle(quote(sigma~"="~2)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

sp4 <- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 4)$gen(300, computed = select(ori_dat, x))) +
  ggtitle(quote(sigma~"="~4)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r example-poly-lineup, fig.height=7, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup[["poly_24"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r different-shape-of-heter, fig.height=2.67, fig.cap="Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

ori_dat <- heter_model(a = -1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300)

hp1 <- VI_MODEL$plot(ori_dat) +
  ggtitle(quote("A. a = -1: Left-triangle")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

hp2 <- VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("B. a = 0: Butterfly")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

hp3 <- VI_MODEL$plot(heter_model(a = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("C. a = 1: Right-triangle")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r different-b, fig.height = 2, fig.cap="Five different values of $b$ are used in experiment II to control the strength of the signal."}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

ori_dat <- heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 0.25)$gen(300)

bp1 <- VI_MODEL$plot(ori_dat) +
  ggtitle(quote("b = 0.25")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

bp2 <- VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 1)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 1")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

bp3 <- VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 4)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 4")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

bp4 <- VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 16)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 16")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

>>>>

@@

Effect $E$ is derived from the Kullback-Leibler divergence (see Appendix for the details) formulated as

@@

\begin{gather}  \label{eq:effect-size}
E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

@@

To study various factors contributing to the power of the visual test, the same logistic regression model is fit on different subsets of the collated data grouped by levels of factors. These include the distribution of the regressor and the type of the simulated model (modify this according to the result).

@@

Three experiments are conducted to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. Meanwhile, the experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test. The experiment III is designed for collecting human responses to null lineups such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to collect `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three experiments.

@@

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", ""),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rcrrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Description of all factors involved in the non-linear and heteroskedasticity studies.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Heteroskedasticity Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Heteroskedasticity (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)")) %>% #"Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
```

@@

```{r different-shape-of-herimite, fig.height = 2, fig.cap="Polynomial forms generated for the residual plots used in experiment I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$."}

# Data for shape 1
ori_dat <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.05)$gen(300)

# Plot data for shape 1
pp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(He[2]:"U")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for shape 2. Reuse x and e.
pp2 <- poly_model(shape = 2, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(He[3]:"S")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for shape 3. Reuse x and e.
pp3 <- poly_model(shape = 3, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(He[6]:"M")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for shape 4. Reuse x and e.
pp4 <- poly_model(shape = 4, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(He[18]:"Triple-U")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r different-dist, fig.height = 2, fig.cap="Variations in fitted values ($X_{raw}$), that might affect perception of residual plots. Four different distribution are used."}

# Data for uniform distribution
ori_dat <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.5)$gen(300)

# Plot the data for uniform distribution
dp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle("A. Uniform") + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for normal distribution
dp2 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_normal(sigma = 0.3); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.5)$
  gen(300, computed = select(ori_dat, e)) %>%
  VI_MODEL$plot() +
  ggtitle("B. Normal") +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for lognormal distribution
dp3 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_lognormal(sigma = 0.6);
                    closed_form(~stand_dist(raw_x/3 - 1))
                    }, 
                  sigma = 0.5)$
  gen(300, computed = select(ori_dat, e)) %>%
  VI_MODEL$plot() +
  ggtitle("C. Skewed") +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for discrete uniform distribution
dp4 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform_d(k = 5, even = TRUE);
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.5)$
  gen(300, computed = select(ori_dat, e)) %>%
  VI_MODEL$plot() +
  ggtitle("D. Discrete") +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r different-n, fig.height = 2.67, fig.cap="Three different values of $n$ are used in experiment I, II and III to control the strength of the signal."}

# Generate data for 300 observations
ori_dat <- poly_model(shape = 2, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 1.5)$gen(300)

# Plot data for 300 observations
np300 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(n~"="~300)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for 50 observations
np50 <- poly_model(shape = 2, 
                   x = {
                     raw_x <- rand_uniform(-1, 1);
                     closed_form(~stand_dist(raw_x))
                     }, 
                   sigma = 1.5)$
  gen(50, computed = select(ori_dat[1:50, ], x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(n~"="~50)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for 100 observations
np100 <- poly_model(shape = 2, 
                    x = {
                      raw_x <- rand_uniform(-1, 1);
                      closed_form(~stand_dist(raw_x))
                      }, 
                    sigma = 1.5)$
  gen(50, computed = select(ori_dat[1:100,], x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(n~"="~100)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(np50, np100, np300, ncol = 3)
```

```{r different-sigma, fig.height = 2, fig.cap="Four different values of $\\sigma$ are used in the experiment I to control the strength of the signal."}

# Generate data for sigma 0.5
ori_dat <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.5)$gen(300)

# Plot data for sigma 0.5
sp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(sigma~"="~0.5)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for sigma 1
sp2 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 1)$
  gen(300, computed = select(ori_dat, x)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(sigma~"="~1)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for sigma 2
sp3 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 2)$
  gen(300, computed = select(ori_dat, x)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(sigma~"="~2)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for sigma 4
sp4 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 4)$
  gen(300, computed = select(ori_dat, x)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(sigma~"="~4)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r example-poly-lineup, fig.height=7, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r different-shape-of-heter, fig.height=2.67, fig.cap="Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

# Generate data for a = -1
ori_dat <- heter_model(a = -1, 
                       x = {
                         raw_x <- rand_uniform(-1, 1);
                         closed_form(~stand_dist(raw_x))
                         }, 
                       b = 128)$gen(300)

# Plot data for a = -1
hp1 <- VI_MODEL$plot(ori_dat) +
  ggtitle(quote("A. a = -1: Left-triangle")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Plot data for a = 0
hp2 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 128)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("B. a = 0: Butterfly")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Plot data for a = 1
hp3 <- heter_model(a = 1, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 128)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("C. a = 1: Right-triangle")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

@@

```{r different-b, fig.height = 2, fig.cap="Five different values of $b$ are used in experiment II to control the strength of the signal."}

# Generate data for b = 0.25
ori_dat <- heter_model(a = 0, 
                       x = {
                         raw_x <- rand_uniform(-1, 1);
                         closed_form(~stand_dist(raw_x))
                         }, 
                       b = 0.25)$gen(300)

# Plot data for b = 0.25
bp1 <- VI_MODEL$plot(ori_dat) +
  ggtitle(quote("b = 0.25")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for b = 1
bp2 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 1)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 1")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for b = 4
bp3 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 4)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 4")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate data and plot data for b = 16
bp4 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 16)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 16")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
